### 2021-01-15 README.Rmd
debug examples, update readme

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

```{r}
# Fit model with cross-validation
ex_bw <- focal_vs_comp_ex %>%
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid_sf) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

>>>>

# Get predicted dbh values values
predictions <- 
  posterior_param_ex$fe_data %>%
  select(focal_ID, focal_sp, dbh, growth) %>%
  distinct() %>%
  bind_cols(predict(posterior_param_ex))

@@

```{r}
# Fit model with cross-validation
ex_bw <- posterior_param_ex %>%
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid_sf) %>%
  bind_cols(
    posterior_param_ex$fe_data %>%
    select(focal_ID, focal_sp, dbh, growth) %>%
    distinct()
  )
